Explicit B-spline regularization in diffeomorphic image registration

### 2013-11-01 paper.tex
BUG:  Missed parentheses.
BUG:  Another missed parentheses.

Continuing from the work of \cite{christensen1996} and subsequent
exploration into the mathematical formalisms of diffeomorphisms
\citep[e.g.][]{dupuis1998}, the well-known Large Deformation
Diffeomorphic Metric Mapping (LDDMM) algorithm was proposed in
\cite{beg2005}.  In contrast to the mapping produced by
\cite{christensen1996}, LDDMM yields the geodesic solution in the
space of diffeomorphisms between two images. Since its introduction,
LDDMM has inspired much innovation in the image registration
literature.  Applying the log-Euclidean framework of
\cite{arsigny2006}, DARTEL (Diffeomorphic Anatomic Registration using
Exponential Lie algebra) uses a constant velocity field
parameterization to provide a fast, diffeomorphic alternative
\citep{ashburner2007}. Additionally, symmetrical considerations in the
velocity field parameterization are discussed in \cite{avants2008} in
the context of a cross correlation similarity metric.  By explicitly
symmetrizing the LDDMM formulation, this Symmetric Normalization (SyN)
minimizes the bias of the resulting transformation when selecting the
``fixed'' and ``moving'' images.  A greedy version of this algorithm
has proven successful in neuroimaging \citep{klein2009} and pulmonary
\citep{murphy2011} applications as well as in multi-atlas label fusion \cite{wang2012}.

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{labels.jpg}
  \caption{Axial views of sample labelings for a member of each data set.  
  The second row consists of the original labelings with the third row being
  refined versions of those labelings using the MALF algorithm \cite{wang2012}.
  These refinements provide more consistency between labelings and improved
  comparative assessments between algorithms.
  }
  \label{fig:labels}
\end{figure}

>>>>

Continuing from the work of \cite{christensen1996} and subsequent
exploration into the mathematical formalisms of diffeomorphisms
\citep[e.g.][]{dupuis1998}, the well-known Large Deformation
Diffeomorphic Metric Mapping (LDDMM) algorithm was proposed in
\cite{beg2005}.  In contrast to the mapping produced by
\cite{christensen1996}, LDDMM yields the geodesic solution in the
space of diffeomorphisms between two images. Since its introduction,
LDDMM has inspired much innovation in the image registration
literature.  Applying the log-Euclidean framework of
\cite{arsigny2006}, DARTEL (Diffeomorphic Anatomic Registration using
Exponential Lie algebra) uses a constant velocity field
parameterization to provide a fast, diffeomorphic alternative
\citep{ashburner2007}. Additionally, symmetrical considerations in the
velocity field parameterization are discussed in \cite{avants2008} in
the context of a cross correlation similarity metric.  By explicitly
symmetrizing the LDDMM formulation, this Symmetric Normalization (SyN)
minimizes the bias of the resulting transformation when selecting the
``fixed'' and ``moving'' images.  A greedy version of this algorithm
has proven successful in neuroimaging \citep{klein2009} and pulmonary
\citep{murphy2011} applications as well as in multi-atlas label fusion \citep{wang2012}.

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{labels.jpg}
  \caption{Axial views of sample labelings for a member of each data set.  
  The second row consists of the original labelings with the third row being
  refined versions of those labelings using the MALF algorithm \citep{wang2012}.
  These refinements provide more consistency between labelings and improved
  comparative assessments between algorithms.
  }
  \label{fig:labels}
\end{figure}
